Paper round 2 simplified

### 2018-12-04 paper_round2.Rmd
commit paper round 2
include FP Molina as author

---
title: "Paper round 2"
author: "Ainhoa Magrach"
date: "6 November 2018"
output: html_document
bibliography: library.bib
---

---
title: Impact of interaction network structure on community-level plant reproductive success 
author: "Magrach, A & Bartomeus, I"
date: "6 November 2018"
output: html_document
---

@@

#no significant differences

>>>>

---
title: "Paper round 2 simplified"
author: "Magrach, A, Molina, FP, Bartomeus, I"
date: "6 November 2018"
output: html_document
bibliography: library.bib
---

---
title: Impact of interaction network structure on community-level plant reproductive success 
author: "Magrach, A, Molina, FP, Bartomeus, I"
date: "6 November 2018"
output: html_document
---

@@

#permanova... we need to control for the web, right? not sure what you mean here, random effect?

adonis(mp2[,3:48]~ mean.fruitset, data=mp2, method = "euclidean", strata = mp2$web)
adonis(mp2[,3:48]~ class, data=mp2, method = "bray")

#no significant differences at all.
